\cvsection{Experience}

\begin{cventries}
  \cventry
    {Staff DevOps Engineer} % Job title
    {Evidation Health} % Organization
    {Remote} % Location
    {February 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          {I maintain and deploy a pure cloud based infrastructure for medical and health analysis in AWS and Heroku. We utilize terraform, saltstack, and ansible for configuration and infrastructure management. \\~\\ Major personal accomplishments include leading the work to migrate our entire software stack to containerization utilizing docker and ECS as well as migrating every team to Jenkins Pipelines for CI/CD. \\~\\ Backend services are Python/Flask and Ruby on Rails. Supported frontend development in React.}
      \end{cvitems}
    }

  \cventry
    {Senior DevOps Engineer} % Job title
    {Lastline, Inc} % Organization
    {Goleta, CA} % Location
    {May 2014 - February 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        { Worked on the design of as well as the deployment and management of a large-scale, hybrid infrastructure that supports the analysis of malware and the global deployment of network security systems. \\~\\ Led the effort to replace a large NFS system with ceph for large-scale object storage. \\~\\ Managed configurations in the Linux environment using Puppet, Ansible, and Fabric. }
      \end{cvitems}
    }

  \cventry
    {Senior Systems and Security Engineer} % Job title
    {IBrand, LLC} % Organization
    {Calabasas,, CA} % Location
    {Jan 2012 - August 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        { Main responsibilities include design, installation, configuration, monitoring, and threat management in a Linux environment. }
      \end{cvitems}
    }

  \cventry
    {Network Security Engineer} % Job title
    {United States Navy} % Organization
    {Numerous Locations, Worldwide} % Location
    {February 2005 - February 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Supervised team of 3 network security analysts. Designed, developed, and implemented high availability clustered NIDS, HIDS, and Inline IPS systems. \\~\\ Led network security systems integration, datacenter infrastructure, and managed networking for a several thousand host network.}
      \end{cvitems}
    }    
\end{cventries}
